Toxic Code Snippets on Stack Overflow

### 2018-05-20 cloverflow-tse/cover_letter/cover_letter.tex
The complete draft of the cover letter and the TSE paper.

To measure the impact of this minimum clone size threshold on the clone results, 
we performed an investigation of three different threshold values: six, ten, and fifteen lines. 
We started the investigation by using a minimum clone size of six lines, a
well-accepted minimum clone size in clone benchmark~\cite{Bellon2007}. Simian
reported 67,172 clone candidate pairs and SourcererCC reported 7,752 clone
candidate pairs. We randomly sampled 382 pairs from the two sets and the first
author investigated them. This was a statistical significant sample with a 95\%
confidence level and $\pm 5\%$ confidence interval. We found 26 non-clone pairs;
322 trivial clone pairs including \texttt{equals}, \texttt{hashCode}, or
getters/setters; and 34 non-trivial clone pairs. Next, we increased the minimum
clone size to ten lines, another well-established minimum clone size for
large-scale data sets~\cite{Sajnani2016}, and retrieved 721 clone pairs from
Simian and 1,678 clone pairs from SourcererCC. We randomly sampled and manually
checked the same amount of 382 pairs and found 27 non-clone pairs, 253 trivial
clone pairs and 102 non-trivial clone pairs. Then, we increased the minimum
clone size further to fifteen lines and retrieved 196 clone pairs from Simian
and 1,230 clone pairs from SourcererCC. The manual check of the 382 randomly
sampled pairs reveal zero non-clone pairs, 298 trivial clone pairs and 83
non-trivial clone pairs.

The findings from the three samples show that selecting the minimum of ten lines
was a sweet spot and was preferred over six and fifteen lines. First, it generated 
a fewer number of clone pairs than using six lines, which made the manual clone
investigation feasible. Second, it preserved the highest number of non-trivial clone
pairs.

>>>>

To measure the impact of this minimum clone size threshold on the clone results, 
we performed an investigation of three different threshold values: six, ten, and fifteen lines. 
We started our investigation by using a threshold value of six
lines, a well-accepted minimum clone size in clone benchmark~\cite{Bellon2007}.
Simian reported 67,172 clone candidate pairs and SourcererCC reported 7,752
clone candidate pairs. We randomly sampled 382 pairs from the two sets for
manual check. This sample amount was a statistical significant sample with a
95\% confidence level and $\pm 5\%$ confidence interval. The first author
investigated the sampled clone pairs and classified them into three groups:
non-clones, trivial clones (\texttt{equals}, \texttt{hashCode}, or getter and
setter methods), and non-trivial clones. The manual check found 26 non-clone
pairs; 322 trivial clone pairs and 34 non-trivial clone pairs. Next, we increased the
threshold to ten lines, another well-established minimum clone size for
large-scale data sets~\cite{Sajnani2016}, and retrieved 721 clone pairs from
Simian and 1,678 clone pairs from SourcererCC. We randomly sampled and manually
checked the same amount of 382 pairs and found 27 non-clone pairs, 253 trivial
clone pairs and 102 non-trivial clone pairs. Then, we increased the threshold
further to fifteen lines and retrieved 196 clone pairs from Simian and 1,230
clone pairs from SourcererCC. The manual check of the 382 randomly sampled pairs
reveal zero non-clone pairs, 298 trivial clone pairs and 83 non-trivial clone
pairs.

The findings from the three threshold values show that selecting the minimum clone size 
of ten lines was preferred over six and fifteen lines. First, it generated 
a fewer number of clone pairs than using six lines, which made the manual clone
investigation feasible. Second, it preserved the highest number of non-trivial clone
pairs.
